Decompositions of congruence subgroups of Chevalley groups

### 2015-11-09 paper.tex
Small fixes

\definecolor{darkblue}{rgb}{0.0, 0.0, 0.55}

\hypersetup{
  pdfauthor={Sergey Sinchuk, Andrei Smolensky},
  pdftitle={Decompositions of congruence subgroups of Chevalley groups},  
  colorlinks=true,
  urlcolor=darkblue}

@@

\title [Decompositions of congruence subgroups of Chevalley groups] {Decompositions of congruence subgroups \\ of Chevalley groups}
\keywords {parabolic decomposition, bounded generation, $\SL_2$-factorization, product decomposition. {\em Mathematical Subject Classification (2010):} 20G40, 20G35, 19B14}
\author{Sergey Sinchuk}
\author{Andrei Smolensky}
\email{sinchukss {\it at} yandex.ru; andrei.smolensky {\it at} gmail.com}
\thanks{Authors of the present paper acknowledge the financial support from Russian Science Foundation grant 14-11-00297}

@@

The next main result is the relative Dennis---Vaserstein decomposition, which holds for a broader class of rings as compared to \cref{thm:srRI1}.
\begin{thm}\label{thm:DennisVaserstein}
Let $\Phi \neq \rE_8$ be a reduced irreducible root system of rank $\ell\geq 2$ and let $\{ r, s \}$ be a pair of distinct terminal vertices of the Dynkin diagram of $\Phi$. Denote the distance between $r$ and $s$ by $d$.
Assume that $\Phi$, $I$ and $\{r, s\}$ satisfy either of the following assumptions:
\begin{thmlist}
 \item $\sr(I) \leqslant d$ for classical $\Phi$,
 \item $\sr(I) \leqslant d$ for $\Phi=\rE_\ell$ with $\{r, s\} = \{ 2, \ell \}$.
 \item $\asr(I) \leqslant d$ for $\Phi=\rE_\ell$ with $\{r, s\} = \{1, \ell \}$,
 \item $\asr(I) \leqslant d$ for $\Phi=\rF_4$.
\end{thmlist}
Then $\E(\Phi, R, I) = \EP_r(R, I) \cdot \U(\Sigma^-_r \cap \Sigma^-_s, I) \cdot \EP_s(R, I).$ \end{thm}
Even in the special case $I=R$ the above theorem contains several new cases as compared to~\cite[Theorems~2.5 and~4.1]{St78}.
The term ``Dennis---Vaserstein decomposition'' is due to A.~Suslin and M.~Tulenbaev (cf.~\cite[Lemma~2.1]{ST76}).

>>>>

\definecolor{darkblue}{rgb}{0.0, 0.0, 0.6}

\hypersetup{
  pdfauthor={Sergey Sinchuk, Andrei Smolensky},
  pdftitle={Decompositions of congruence subgroups of Chevalley groups},  
  colorlinks=true,
  urlcolor=darkblue,
  linkcolor=darkblue,
  citecolor=darkblue}

@@

\title [Decompositions of congruence subgroups of Chevalley groups] {Decompositions of congruence subgroups \\ of Chevalley groups}
\keywords {parabolic decomposition, bounded generation, $\SL_2$-factorization, subsystem factorization, product decomposition. {\em Mathematical Subject Classification (2010):} 20G40, 20G35, 19B14}
\author{Sergey Sinchuk}
\author{Andrei Smolensky}
\email{sinchukss {\it at} yandex.ru; andrei.smolensky {\it at} gmail.com}
\thanks{Authors of the present paper acknowledge the financial support from Russian Science Foundation grant 14-11-00297}

@@

The next main result is the relative Dennis---Vaserstein decomposition, which holds for a broader class of rings as compared to \cref{thm:srRI1}.
\begin{thm}\label{thm:DennisVaserstein}
Let $\Phi \neq \rE_8$ be a reduced irreducible root system of rank $\ell\geqslant 2$ and let $\{ r, s \}$ be a pair of distinct terminal vertices of the Dynkin diagram of $\Phi$. Denote the distance between $r$ and $s$ by $d$.
Assume that $\Phi$, $I$ and $\{r, s\}$ satisfy either of the following assumptions:
\begin{thmlist}
 \item $\sr(I) \leqslant d$ for classical $\Phi$,
 \item $\sr(I) \leqslant d$ for $\Phi=\rE_\ell$ with $\{r, s\} = \{ 2, \ell \}$.
 \item $\asr(I) \leqslant d$ for $\Phi=\rE_\ell$ with $\{r, s\} = \{1, \ell \}$,
 \item $\asr(I) \leqslant d$ for $\Phi=\rF_4$.
\end{thmlist}
Then $\E(\Phi, R, I) = \EP_r(R, I) \cdot \U(\Sigma^-_r \cap \Sigma^-_s, I) \cdot \EP_s(R, I).$ \end{thm}
Even in the special case $I=R$ the above theorem contains several new cases as compared to~\cite[Theorems~2.5 and~4.1]{St78}.
The term ``Dennis---Vaserstein decomposition'' is due to A.~Suslin and M.~Tulenbaev (cf.~\cite[Lemma~2.1]{ST76}).
